\documentclass{article} 
\parskip 3mm
\usepackage{amsmath}
\newcommand{\nd}{\noindent}
\begin{document}
\title{PHYSICS QUESTIONS} 
\author{Tanmay Agarwal} 
\date{}
\maketitle
\section{Tensor Physics} 
1. Derive the Affine connections 

\nd 2. Show that the transformation of affine connections is not a tensor 

\nd 3. Write the different transformations of covariant tensors 

\nd 4. Write the different transformations of contra-variant tensors 

\nd 5. Define the co-variant derivative in all forms of tensors 

\nd 6. Derive the christoffer symbols 
tron mbo trms
\nd 7. Define the notation for laplacian in tensor notations

\nd 8. Derive the Divergence in tensor notations 

\nd 9. Define the relation between $A^{'}$ and $A$ vectors 

\nd 10. Derive the metric tensor for cylindrical and spherical co-ordinates 

\nd 11. Derive the divergence in spherical co-ordinates

\nd 12. Derive the divergence in Cylindrical co-ordinates

\nd 13. Derive the laplacian in Spherical co-ordinates 

\nd 14. Derive the laplacian in Cylindrical co-ordinates 

\nd 15. Derive the complete curvature tensor and show its transformations 

\nd 16. Define the metric tensor
\newpage

\section{Quantum Mechanics}
1. Define the theorem of superposition of different states 

\nd 2. Define the basis of eigen states as a integral over fourier transforms 

\nd 3. Define the symmetry rules for an infinitesimal change in $f(x)$

\nd 4. Write down the expansion of basis in the position space 

\nd 5. Define in detail the Bra-Ket notations 

\nd 6. Write about the role of probabilities in Quantum Physics 

\nd 7. Define about normalization of the wave function 

\nd 8. Explain in detail about the formation of wavefunction 

\nd 9. Define the operators of momentum and energy 

\nd 10, Define the energy eigen value equations

\nd 11. Derive the time dependent wavefunction for energy eigen functions 

\nd 

\begin{equation}
(\frac{mw}{\hbar \pi})^{\frac{1}{4}} (\frac{1}{\sqrt{2!n!}}H_n(\sqrt{\frac{mw}{e}} x)e^{-\frac{mwx^2}{2\hbar}})
\end{equation}
 
\end{document}